\color{navyblue} Differences-in-Differences with Spatial Spillover

### 2020-11-28 latex/paper/Spillover.tex
Add figure of effective sample and spill vars

This paper first introduces a potential outcome framework that explicitly models this violation of SUTVA following \citet{Vazquez-Bare_2019}. In the presence of spatial spillovers, I identify two sources of bias that result when estimating treatment effects by standard difference-in-differences methodologies.

@@

I extend their analysis to include spatial spillovers in the difference-in-differences specification. To parametrize the exposure mapping, I include a set of indicator variables for being in distance bins away from the Authority. I do this for two reasons. Specifically, I use the following intervals $\text{Dist} = \{(0, 50], (50, 100], (100, 150]\}$ measured in miles and define $\text{Between}(d)$ as an indicator for being within the interval $d \in \text{Dist}$ away from the Authority. As discussed above, I suspect the spillover effects to change with distance to the authority, hence I allow the effect to be seperately identified in bins. I keep the number of bins small to improve precision of spillover estimates.

The specification with spillovers is given as follows:  
\begin{equation}\label{eq:tva_spillover}
    y_{i, 2000} - y_{i, 1940} = \alpha + \text{TVA}_i \tau + \sum_{d \in \text{Dist}} \text{Between}(d)\delta_d + X_{i, 1940} \beta + (\varepsilon_{i, 2000} - \varepsilon_{i, 1940})
\end{equation} 
The coefficients $\delta_d$ measure the spillover effect onto control units at different distances from the Authority. If specification \ref{eq:tva_spillover} is correctly specified, then $\hat{\tau}$ will be an unbiased estimate for the `local' effect. As shown above, minor misspecification will remove some but not all of the bias from standard difference-in-differences estimates.

>>>>

This paper identifies problems in estimation of treatment effets in the presence of spillovers and provides practical advice on using specifications that are robust to spillovers.

To do this, I first introduces a potential outcome framework that explicitly models this violation of SUTVA following \citet{Vazquez-Bare_2019}. In the presence of spatial spillovers, I identify two sources of bias that result when estimating treatment effects by standard difference-in-differences methodologies.

@@

In order to more likely satisfy the paralell trends assumption, the run a logistic regression to predict being in the TVA based on their set of control variables $X_{c, pre}$ and keep only observations in the top 75\% of predicted probability. The counties used in the sample are presented in Figure \ref{fig:tva_sample}.

\begin{figure}[tbh!]
    \caption{TVA Effective Sample and Spillover Variables}
    \label{fig:tva_sample}

    {\centering
        \resizebox{\textwidth}{!}{
            \includegraphics{../../figures/figure-tva-sample.pdf}
        } 
    }

    {\footnotesize \textit{Notes:} The above figure plots all the counties used in the estimation. Counties that fall within the distance intervals $\{(0, 50], (50, 100], (100, 150]\}$ measured in miles are colored by their respective bin.}
\end{figure}

I extend their analysis to include spatial spillovers in the difference-in-differences specification. To parametrize the exposure mapping, I include a set of indicator variables for being in distance bins away from the Authority. I do this for two reasons. Specifically, I use the following intervals $\text{Dist} = \{(0, 50], (50, 100], (100, 150]\}$ measured in miles and define $\text{Between}(d)$ as an indicator for being within the interval $d \in \text{Dist}$ away from the Authority. Figure \ref{fig:tva_sample} displays the three spillover variables by filling in each distance bin in a different color. As discussed above, I suspect the spillover effects to change with distance to the Authority, hence I allow the effect to be seperately identified in bins. I keep the number of bins small to improve precision of spillover estimates.

The specification with spillovers is given as follows:  
\begin{equation}\label{eq:tva_spillover}
    y_{i, 2000} - y_{i, 1940} = \alpha + \text{TVA}_i \tau + \sum_{d \in \text{Dist}} \text{Between}(d)\delta_d + X_{i, 1940} \beta + (\varepsilon_{i, 2000} - \varepsilon_{i, 1940})
\end{equation} 
The coefficients $\delta_d$ measure the spillover effect onto control units at different distances from the Authority. If specification \ref{eq:tva_spillover} is correctly specified, then $\hat{\tau}$ will be an unbiased estimate for what the authors call the `local' effect. As shown above, minor misspecification will remove some but not all of the bias from standard difference-in-differences estimates.

The results of the analysis are presented in Table \ref{tab:tva}. The first column lists which dependent variable (measured in logs) was used in the row. The following columns contain point estimates for $\tau$ and $\delta_s$ in different specifications and can be interpreted as decadel growth rates in outcomes. The column labeled `Kline \& Moretti (2011)' use an Oaxaca-Blinder estimator while the column labeled difference-in-differences uses an ordinary least squares estimator for Equation \ref{eq:tva}. The two columns are very close in magnitude to each other. They find a decline in agricultural employment of about $5.6\%$ per decade, an increase in manufacturing employment of about $6.1\%$ per decade, and an increase in median family income of about $2.2\%$ per decade.
